### 2022-06-16 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@9589ee267f240de2621beeb994006c7e11f55c85 🚀

Bats are found worldwide and are both one of the most diverse groups
among mammals (\textbf{Moratelli \& Calisher, 2015}), and one of the
main animal reservoir for different strains of betacoronaviruses
(Drexler et al. 2014). This has attracted attention to areas where high
diversity of bats, and therefore presumably high diversity of
betacoronaviruses, can be an important issue for human health (Calisher
et al. 2006, Moratelli and Calisher 2015). By overlaying the IUCN
rangempas for confirmed bat hosts of betacoronaviruses
{[}fig.~\ref{fig:richness}; top{]}, we see that the the main hotspots of
host richness are primarily South-Eastern Asia, parts of Southern
Europe, and to a lesser extent parts of Africa in the -25-0 range of
latitudes. The description of host richness is an important first step
towards understanding risk, as previous research (Anthony et al. 2017,
Mollentze and Streicker 2020) states that locally diverse bat
communities could maintain more viruses and hence, a higher probability
of having a pathogen that could represent a risk for human health.

>>>>

Bats are found worldwide and are both one of the most diverse groups
among mammals and one of the main animal reservoir for different strains
of betacoronaviruses (Drexler et al. 2014). This has attracted attention
to areas where high diversity of bats, and therefore presumably high
diversity of betacoronaviruses, can be an important issue for human
health (Calisher et al. 2006, Moratelli and Calisher 2015). By
overlaying the IUCN rangempas for confirmed bat hosts of
betacoronaviruses {[}fig.~\ref{fig:richness}; top{]}, we see that the
the main hotspots of host richness are primarily South-Eastern Asia,
parts of Southern Europe, and to a lesser extent parts of Africa in the
-25-0 range of latitudes. The description of host richness is an
important first step towards understanding risk, as previous research
(Anthony et al. 2017, Mollentze and Streicker 2020) states that locally
diverse bat communities could maintain more viruses and hence, a higher
probability of having a pathogen that could represent a risk for human
health.
